Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-09-01 main/doc/chord_sysprops.tex
replaced chord.publish.results -> chord.print.results and chord.publish.targets -> chord.print.project

\item
\code{chord.publish.targets} \\
{\bf Type:} bool \\
{\bf Description:} Create files \code{targets_sortby_name.html}, \code{targets_sortby_kind.html}, and \code{targets_sortby_producers.html} in directory \code{[chord.out.dir]}, publishing all targets defined by program analyses in paths \code{[chord.java.analysis.path]} and \code{[chord.dlog.analysis.path]}. \\
{\bf Default value:} {\tt false}
\end{itemize}

@@

\item
\code{chord.publish.results} \\
{\bf Type:} bool \\
{\bf Description:} Publish the results of program analyses in HTML.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} {\tt true}

@@

\item
\code{chord.javadoc.url} \\
{\bf Type:} string \\
{\bf Description:} URL of the Javadoc location of program analyses.  It is used when publishing targets (i.e., when property \code{chord.publish.targets} is set to {\tt true}). \\
{\bf Default value:} \code{http://jchord.googlecode.com/svn/wiki/javadoc/}
\end{itemize}

>>>>

\item
\code{chord.print.project} \\
{\bf Type:} bool \\
{\bf Description:} Create files \code{targets_sortby_name.html}, \code{targets_sortby_kind.html}, and \code{targets_sortby_producers.html} in directory \code{[chord.out.dir]}, publishing all tasks and targets defined by program analyses in paths \code{[chord.java.analysis.path]} and \code{[chord.dlog.analysis.path]}. \\
{\bf Default value:} {\tt false}
\end{itemize}

@@

\item
\code{chord.print.results} \\
{\bf Type:} bool \\
{\bf Description:} Print the results of program analyses in HTML.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} {\tt true}

@@

\item
\code{chord.javadoc.url} \\
{\bf Type:} string \\
{\bf Description:} URL of the Javadoc location of program analyses.  It is used when printing the project (i.e., when property \code{chord.print.project} is set to {\tt true}). \\
{\bf Default value:} \code{http://jchord.googlecode.com/svn/wiki/javadoc/}
\end{itemize}
